---
title: "Compilation"
author: "Emily Lacroix"
date: "2025-JAN-09"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script:

* combines all data (see `CompositeFigure.Rmd` and `ddPCR-allgenes.Rmd` for source of electro and ddPCR csv's, respectively)
* perform a PCA on all of the rough indicators for reducing conditions 
* see if this metric for reducing conditions correlates with anything/varies predictably by depth or position 

# Set-up

## Libraries

```{r echo=TRUE, results ='hide', warning=FALSE, message=FALSE}
library(ggpattern)
library(ggfortify)
library(ggrepel)
library(corrplot)
library(outliers)
library(tidyverse)
library(readxl)
library(car)

```

## Files

```{r eval=FALSE}

fe_edc_eac_file <- "compiled_fe_edc_eac_v2.csv"

ddpcr_file <- "compiled_ddpcr.csv"

ea_analysis_file <- "TCTN_data_raw.xlsx"

```


```{r eval=TRUE, echo=FALSE}

fe_edc_eac_file <- "/Users/elacroi3/Documents/Research/Aggregate-dish/Data/Compilation/compiled_fe_edc_eac_v2.csv"

ddpcr_file <- "/Users/elacroi3/Documents/Research/Aggregate-dish/Data/Compilation/compiled_ddpcr.csv"

ea_analysis_file <- "/Users/elacroi3/Documents/Research/Aggregate-dish/Data/TCTN_data_raw.xlsx"

```


## Constants

```{r}
site_colors <- c("R" = "darkgoldenrod1", "T" = "darkblue")

site_names <- c("R" = "Sandy Loam", "T" = "Loam")

agg_names <- c("B" = "Bulk soil", "IN" = "Agg. Interior")

agg_shapes <- c("Bulk" = 19, "In" = 2)

agg_alpha <- c("B" = 1, "IN" = 0.5)

```

## Figure Theme
```{r}
my_theme <- function(base_size = 10, base_family = ""){ ## Control base font face and size. use `rel()` for relative font size.
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      strip.text = element_text(size = 10, face = "bold"),
      axis.text = element_text(size = 10),
      axis.text.x = element_text(size = 10),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.title = element_text(size = 12),
      strip.background = element_rect(fill = "transparent"),

      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      aspect.ratio = 1.5
    )
}
```

## Import and Combine

```{r warning=FALSE, message=FALSE}

electro_fe <- fe_edc_eac_file %>% read_csv()

tc_tn <-
  ea_analysis_file %>% 
  read_xlsx(skip = 5) %>% 
  select(
    date = `...1`,
    sample = `...2`,
    perc_n = `...7`,
    perc_c = `...8`
  ) %>% 
  filter(str_detect(sample, "-")) %>% 
  separate(sample, into = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(across(rep, as.numeric))



ddpcr <- ddpcr_file %>% read_csv()


all_data <- 
  electro_fe %>% 
  left_join(tc_tn, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  left_join(
    ddpcr %>% 
      mutate(across(bulk_agg, ~ if_else(. == "B", "Bulk", "In"))), 
    by = c("site", "hzn", "rep", "bulk_agg")
  )


```

# PCA

## Check normality and outliers

We want to perform a PCA on all of our indicators for anoxic conditions, including:

* `eac_to_eec` 
* `nirk_copies_per_g`
* `nirs_copies_per_g`
* `mcra_copies_per_g`

Thus, we need to transform these data to be normal and then remove outliers. 

### EAC to EEC

#### Before transformation
```{r}

all_data %>% 
  ggplot(aes(x = eac_to_eec)) + 
  geom_histogram()

```

```{r}

all_data %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec
  ) %>% 
  pull(trans_eac_to_eec) %>% 
  grubbs.test()

```

#### Transformation 

Remove outlier
```{r}

all_data %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec
  ) %>% 
  filter(trans_eac_to_eec > 0.85) %>% # this is from the high EDC value
  pull(trans_eac_to_eec) %>% 
  grubbs.test()

```

```{r}

all_data %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec
  ) %>% 
  filter(trans_eac_to_eec > 0.85) %>% 
  ggplot(aes(x = trans_eac_to_eec)) +
  geom_histogram()

```


```{r}

all_data %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec
  ) %>% 
  filter(trans_eac_to_eec > 0.85) %>% 
  pull(trans_eac_to_eec) %>% 
  shapiro.test()

```
Transformation: Raise to the power of 200

```{r}

all_data %>% 
  filter(eac_to_eec > 0.85) %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec^200
  ) %>% 
  ggplot(aes(x = trans_eac_to_eec)) +
  geom_histogram()


```

```{r}

all_data %>% 
  filter(eac_to_eec > 0.85) %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec^200  
  ) %>% 
  pull(trans_eac_to_eec) %>% 
  shapiro.test()

```



```{r}

all_data %>% 
  filter(eac_to_eec > 0.85) %>% 
  mutate(
    trans_eac_to_eec = eac_to_eec^200  
  ) %>% 
  pull(trans_eac_to_eec) %>% 
  grubbs.test()

```

### nirK per g soil

#### Before transformation

```{r}

all_data %>% 
  ggplot(aes(x = nirk_copies_per_g)) + 
  geom_histogram()

```

#### Transformation

```{r}

all_data %>% 
  ggplot(aes(x = nirk_copies_per_g^(1/3))) + 
  geom_histogram()

```

```{r}

all_data %>% 
  mutate(
    trans_nirk = nirk_copies_per_g^(1/3)
  ) %>% 
  pull(trans_nirk) %>% 
  shapiro.test()

```

```{r}

all_data %>% 
  mutate(
    trans_nirk = nirk_copies_per_g^(1/3)
  ) %>% 
  pull(trans_nirk) %>% 
  grubbs.test()

```

### nirS per g soil

#### Before transformation

```{r}

all_data %>% 
  ggplot(aes(x = nirs_copies_per_g)) + 
  geom_histogram()

```

#### Transformation

```{r}

all_data %>% 
  ggplot(aes(x = nirs_copies_per_g^(1/3))) + 
  geom_histogram()

```

```{r}

all_data %>% 
  mutate(
    trans_nirs = nirs_copies_per_g^(1/3)
  ) %>% 
  pull(trans_nirs) %>% 
  shapiro.test()

```


```{r}

all_data %>% 
  mutate(
    trans_nirs = nirs_copies_per_g^(1/3)
  ) %>% 
  pull(trans_nirs) %>% 
  grubbs.test()

```

### mcrA per g soil 

#### Before transformation

```{r}

all_data %>% 
  ggplot(aes(x = mcra_copies_per_g)) + 
  geom_histogram()

```

#### Transformation

Find lowest non-zero value:

```{r}
all_data %>% 
  filter(mcra_copies_per_g > 0) %>% 
  pull(mcra_copies_per_g) %>% 
  min()

```

Transformation: log10(mcra + 0.5 * lowest non-zero value) 
```{r}

all_data %>% 
  ggplot(aes(x = log10(mcra_copies_per_g + 200))) + 
  geom_histogram()

```

```{r}
all_data %>% 
  mutate(
    trans_mcra = log10(mcra_copies_per_g + 200)
  ) %>% 
  pull(trans_mcra) %>% 
  shapiro.test()

```

```{r}

all_data %>% 
  mutate(
    trans_nirs = log10(mcra_copies_per_g + 200)
  ) %>% 
  pull(trans_nirs) %>% 
  grubbs.test()

```

## Create tibble for PCA

The PCA must transform these variables accordingly: 

* `eac_to_eec` 
    + Remove outlier by retaining values > 0.85
    + Raise to the power of 200
* `nirk_copies_per_g`
    + Cube root
* `nirs_copies_per_g`
    + Cube root
* `mcra_copies_per_g`
    + log10(mcra + 200)

```{r}

pca_tibble <- 
  all_data %>% 
  filter(eac_to_eec > 0.85) %>% # this completely drops the observation
  mutate(
    trans_eac_to_eec = eac_to_eec^200,
    trans_nirk = nirk_copies_per_g^(1/3),
    trans_nirs = nirs_copies_per_g^(1/3),
    trans_mcra = log10(mcra_copies_per_g + 200)
  ) %>% 
  drop_na() %>% 
  mutate(
    across(
      hzn, 
      ~case_when(
        . == "C" ~ "3",
        . == "B" ~ "2",
        . == "A" ~ "1" 
      )
    ) 
  ) 

```

```{r}
pca_microsites <- 
  prcomp(
    ~trans_eac_to_eec + trans_nirk + trans_nirs + trans_mcra, 
    data = pca_tibble, 
    scale = TRUE
  )

```


```{r}

autoplot(
  pca_microsites,
  loadings = TRUE,
  loadings.label = FALSE,
  data = pca_tibble,
  color = "site",
  shape = "bulk_agg",
  size = 6
) +
  geom_text(
    mapping = aes(label = hzn, color = site),
    size = 5,
    data = . %>%  filter(bulk_agg == "In")
  ) +
  geom_text(
    mapping = aes(label = hzn),
    size = 5,
    color = "white",
    data = . %>%  filter(bulk_agg == "Bulk")
  ) +
  scale_color_manual(
    values = site_colors,
    labels = site_names
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) + 
  theme_bw() + 
  theme(
    aspect.ratio = 1,
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16),
    legend.text = element_text(size = 16),
    panel.grid = element_blank()
  ) + 
  labs(
    shape = NULL,
    color = NULL
  )


```


# Relationships between PC1 and Soil Properties

```{r}

pc1 <- 
  pca_microsites$x %>% 
  as_tibble() %>% 
  pull(PC1)

pca1_tibble <- 
  pca_tibble %>% 
  add_column(pc1) 

```


## Soil C Content 

### Linear Model

```{r}

pc1_vs_soilC <- lm(pc1 ~ perc_c, data = pca1_tibble)

pc1_vs_soilC %>% summary()

```


### Figure

```{r}
pca1_tibble %>% 
  ggplot(aes(x = perc_c, y = pc1)) + 
  geom_smooth(method = "lm", se = FALSE, color = "gray", linetype = 2) + 
  geom_point(
    aes(
      shape = bulk_agg,
      color = site
    ),
    size = 5
  ) + 
geom_text(
  mapping = aes(label = hzn, color = site),
  size = 4,
  data = . %>%  filter(bulk_agg == "In")
) +
geom_text(
  mapping = aes(label = hzn),
  size = 4,
  color = "white",
  data = . %>%  filter(bulk_agg == "Bulk")
) +

scale_color_manual(
  values = site_colors,
  labels = site_names
) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  theme(
    aspect.ratio = 1,
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    legend.text = element_text(size = 14)
  ) + 
  labs(
    y = "PC1",
    x = "% Organic C",
    shape = NULL,
    color = NULL
  )

```

## Site Position

```{r}

pca1_tibble %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    avg_pc1 = mean(pc1),
    se_pc1 = sd(pc1) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = avg_pc1, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = avg_pc1 - se_pc1, 
      xmax = avg_pc1 + se_pc1),
    size = 0.8
  ) +
  scale_x_reverse() + # NOTE REVERSE AXIS!!
  scale_y_discrete(limits = rev) +
  scale_color_manual(
    values = site_colors,
    labels = site_names,
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  facet_grid(
    cols = vars(site), 
    scales = "free_x",
    labeller = labeller(site = site_names)
  ) +
  my_theme() +
  theme(
      strip.text = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 12),
      axis.text.x = element_text(size = 12),
      axis.title = element_text(size = 14),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 14),
  ) +
  labs(
    x = "PC1",
    y = "Horizon",
    color = NULL
  )

```

### Statistics

```{r}

pca1_tibble %>% 
  filter(hzn != "3", site == "R") %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    norm = shapiro.test(pc1)$p.value
  )

```

Sandy Loam & Hzn 1
```{r}
var.test(
  x = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "1", bulk_agg == "Bulk") %>% 
    pull(pc1),
  y = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "1", bulk_agg == "In") %>% 
    pull(pc1)
)
```

```{r}
t.test(
  x = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "1", bulk_agg == "Bulk") %>% 
    pull(pc1),
  y = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "1", bulk_agg == "In") %>% 
    pull(pc1),
  var.equal = TRUE
)
```


Sandy Loam & Horizon 2

```{r}
var.test(
  x = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "2", bulk_agg == "Bulk") %>% 
    pull(pc1),
  y = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "2", bulk_agg == "In") %>% 
    pull(pc1)
)
```


```{r}
t.test(
  x = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "2", bulk_agg == "Bulk") %>% 
    pull(pc1),
  y = 
    pca1_tibble %>% 
    filter(site == "R", hzn == "2", bulk_agg == "In") %>% 
    pull(pc1),
  var.equal = TRUE
)
```


# Basic Correlations

Shows that %Carbon is most closely linked with PC1, rather than other indicators


```{r}
cor_test_tibble <- 
  pca1_tibble %>% 
  filter(sixteenS_copies_per_g > 0) %>% 
  filter(eac_to_eec > 0.85) %>% # remove giant outlier from EAC to EEC 
  select(
    fe_ii_umol_per_g,
    edc_umol_g_soil,
    eac_umol_g_soil,
    eac_to_eec,
    perc_n,
    perc_c,
    sixteenS_copies_per_g,
    nirk_copies_per_g,
    nirs_copies_per_g,
    mcra_copies_per_g,
    pc1
  ) %>% 
  rename(
    `Fe(II)` = fe_ii_umol_per_g,
    EAC = eac_umol_g_soil,
    EDC = edc_umol_g_soil,
    `EAC / EEC` = eac_to_eec,
    `% C` = perc_c,
    `% N` = perc_n,
    `16S` = sixteenS_copies_per_g,
    nirK = nirk_copies_per_g,
    nirS = nirs_copies_per_g,
    mcrA = mcra_copies_per_g,
    PC1 = pc1
  )

correlation_matrix <- 
  cor_test_tibble %>% cor(use = "pairwise.complete.obs", method = "spearman")

correlation_p_values <- cor_test_tibble %>% cor.mtest()
```


```{r}

# 
# cor_plot_path =   "[INSERT PATH NAME]"
# 
# png(height=1800, width=1800, file=cor_plot_path, type="quartz")

# Your function to plot image goes here
corrplot(
    correlation_matrix, 
    type = "upper", 
    p.mat = correlation_p_values$p,
    sig.level = 0.05,
    order = "hclust",
    insig = "blank",
    method = "number",
    number.cex = 3,
    cl.cex = 3,
    tl.cex = 3
  )

#dev.off()


```






