---
title: "ddpcr-16s"
author: "Emily Lacroix"
date: "2022-10-26"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

remotes::install_github("coolbutuseless/ggpattern")
```

# Set-up

## Libraries

```{r}
library(ggpattern)
library(tidyverse)
library(readxl)
```


## Files

```{r}

ddpcr_data_file_16s <- "/Users/elacroi3/Documents/Research/Aggregate-dish/Aggregates (copied from GDrive)/ddPCR/Data/EML_16s_09sep2022-manual.csv"

ddpcr_data_file_mcra <- 
  "/Users/elacroi3/Documents/Research/Aggregate-dish/Aggregates (copied from GDrive)/ddPCR/Data/EML_mcrA_01sep2022-manual.csv"

ddpcr_data_file_glta <- 
  "/Users/elacroi3/Documents/Research/Aggregate-dish/Aggregates (copied from GDrive)/ddPCR/Data/gltA_Feb 27/AMG_gltA_27feb2023.csv"
  
ddpcr_data_file_nirk <-
  "/Users/elacroi3/Documents/Research/Aggregate-dish/Aggregates (copied from GDrive)/ddPCR/Data/nirk_1_12_23/AG_nirK_1_12_23.csv"

ddpcr_data_file_nirs <-
"/Users/elacroi3/Documents/Research/Aggregate-dish/Aggregates (copied from GDrive)/ddPCR/Data/nirS_2_10_23/AG_nirS_2-10-23.csv"


ddpcr_grav_data_file <- "/Users/elacroi3/Documents/Research/Aggregate-dish/Data/ddPCR-grav-data.xlsx"

#dna_extraction_file <- 


```


## Constants

```{r}

reaction_volume_df <- 25 #NEED TO INCORPORATE INTO MEASUREMENTS

dna_elution_volume <- 100 #uL

site_colors <- c("R" = "darkgoldenrod1", "T" = "darkblue")

site_names <- c("R" = "Sandy Loam", "T" = "Loam")

agg_names <- c("B" = "Bulk soil", "IN" = "Agg. Interior")

agg_shapes <- c("B" = 15, "IN" = 17)

agg_alpha <- c("B" = 1, "IN" = 0.5)


# g_h2o = mass_g / (1 / avg_gwc + 1),
# mass_dry_soil = mass_g - g_h2o,
# prop = conc / sixteenS_conc,
# copies_per_g_sixteenS = sixteenS_conc * 100 / mass_dry_soil,
# copies_per_g = conc * 100 / mass_dry_soil


```


# Gravimetric data

This code:

* Imports the gravimetric data from an Excel sheet
* Calculates moisture content of samples
* Calculates the dry mass of soil extracted in DNA extractions

```{r}

grav_raw <- 
  read_xlsx(ddpcr_grav_data_file, sheet = "Grav Data from Meret") %>% 
  separate(Sample, into = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    across(rep, as.integer),
    mass_water_per_g_wet_soil = `Mass Water in Soil (g)` / `Mass Wet Soil (g)`
  ) %>% 
  select(site, hzn, rep, mass_water_per_g_wet_soil)




extraction_data <- 
  read_xlsx(ddpcr_grav_data_file, sheet = "DNA Extraction") %>% 
  separate(Sample, into = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(across(rep, as.integer)) %>% 
  rename(mass_extract_wet_g = `Wet mass sample extracted (g)`) %>% 
  left_join(grav_raw, by = c("site", "hzn", "rep")) %>% 
  mutate(
    across(bulk_agg, ~case_match(., "Bulk" ~ "B", "In" ~ "IN")),
    mass_extract_dry_g =
      mass_extract_wet_g - (mass_extract_wet_g * mass_water_per_g_wet_soil)
  ) %>% 
  select(site, hzn, rep, bulk_agg, mass_extract_dry_g)

extraction_data


```




# 16S

This code: 

* Imports the 16S data from a CSV

```{r}

sixteenS_df <- 1000 #NEED TO DOUBLE CHECK WITH DDPCR BINDER

ddpcr_data_16s <- 
  ddpcr_data_file_16s %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg", "dilution")) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    sixteenS_conc = Concentration,
    sixteenS_min = PoissonConfMin,
    sixteenS_max = PoissonConfMax,
    droplets = AcceptedDroplets
  ) %>% 
  filter(
    !(
      is.na(dilution) & 
        samp %in% c("RA3", "RB1", "RB2", "RB3") & 
        bulk_agg == "IN"
      )
  )

ddpcr_data_16s

```


## Check Technical replicates
```{r}

ddpcr_data_16s %>% 
  ggplot(
    aes(x = samp, y = sixteenS_conc, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = sixteenS_min, ymax = sixteenS_max))

```

Technical replicate for TA1 does not look great. Other ones look good though. 

## Adjust conc

This code: 

* Subtracts the counts from the blanks 
* Corrects for DNA template dilution
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)
* Calculates 16S copies per g
* Takes average value for technical replicates

```{r}
blank_16s <- 
  ddpcr_data_16s %>% 
  filter(samp == "TE" | samp == "Water") %>% 
  summarise(mean_blank_16s = mean(sixteenS_conc)) %>% 
  pull(mean_blank_16s)


data_16s_adj <- 
  ddpcr_data_16s %>% 
  filter(samp != "TE" & samp != "Water") %>% 
  mutate(
    blank = blank_16s,
    sixteenS_conc_minus_blank =
      case_when(
        dilution == "1" ~ (sixteenS_conc / 10) - blank,
        TRUE ~ sixteenS_conc - blank
      ),
    across(sixteenS_conc_minus_blank, ~ if_else(. < 0, 0, .)),
    sixteenS_conc_adj = 
      #already accounts for 100 vs. 1000 dilution
      sixteenS_conc_minus_blank * sixteenS_df * reaction_volume_df, 
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = str_extract(samp, ".{1}$")
  ) %>% 
  select(
    site, hzn, rep, bulk_agg, sixteenS_conc_adj, 
    sixteenS_droplets = droplets
  ) %>% 
  mutate(across(rep, as.integer)) %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  left_join(extraction_data, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    sixteenS_copies_per_g = 
      sixteenS_conc_adj * dna_elution_volume / mass_extract_dry_g
  ) %>% 
  summarise(
    across(c(sixteenS_conc_adj, sixteenS_copies_per_g), ~mean(.))
  ) 

data_16s_adj

```

It appears we got no positive amplification (beyond contamination) from RC1-Bulk. I think we'll need to try again or omit from dataset. 

## Copies per g

### technical replicates averaged
```{r}

data_16s_adj %>% 
  ggplot(
    aes(y = hzn, x = sixteenS_copies_per_g, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "16S copies per g soil",
    y = "Horizon"
  )


```

### texture-bulk-hzn averaged

```{r}
data_16s_adj %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_16s = mean(sixteenS_copies_per_g, na.rm = TRUE),
    se_16s = sd(sixteenS_copies_per_g) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_16s, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(xmin = mean_16s - se_16s, xmax = mean_16s + se_16s),
    fatten = 4
  ) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "16S copies per g soil",
    y = "Horizon"
  )

```


### Key take-aways (16S)

* More 16S copies in Loam vs. Sandy Loam soil
* More 16S copies in surface soil & decreases with depth
* Aggregate interiors yield less 16S copies, unclear if this is due to extraction mass or efficiency....


# mcrA

This code: 

* Imports the mcrA data from a CSV
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)

NOTE - one of my technical replicates is really high....need to look at notes from the ddPCR run


```{r}

ddpcr_data_mcra <- 
  ddpcr_data_file_mcra %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg")) %>% 
  select(
    samp, 
    bulk_agg, 
    mcra_conc = Concentration,
    mcra_min = PoissonConfMin,
    mcra_max = PoissonConfMax,
    droplets = AcceptedDroplets
  ) %>% 
  filter(
    !(samp %in% c("Water", "PositiveControl", "buffer")),
    droplets > 10000
  ) %>% 
  mutate(
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    mcra_droplets = droplets,
    across(mcra_conc, as.numeric),
    across(c(mcra_conc, mcra_min, mcra_max), ~ . * reaction_volume_df)
  ) 

ddpcr_data_mcra 
  
```

## Inspect techincal replicates

```{r}

ddpcr_data_mcra %>% 
  ggplot(
    aes(x = samp, y = mcra_conc, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = mcra_min, ymax = mcra_max))

```

RC1-Bulk is seemingly missing..... and the technical replicates for RA1 look horrible. Need to look at ddPCR folder. I would assume that RA1 was failure to generate droplets or something....

For now, let's average the technical replicates

This code

* Takes average value for technical replicates


```{r}

ddpcr_data_mcra_av <- 
  ddpcr_data_mcra %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  left_join(extraction_data, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    mcra_copies_per_g =
      mcra_conc * dna_elution_volume / mass_extract_dry_g
  ) %>% 
  summarise(
    across(c(mcra_conc, mcra_copies_per_g), ~mean(.))
  ) 

ddpcr_data_mcra_av

```


## Copies per g 

### technical replicates averaged

```{r}

ddpcr_data_mcra_av %>% 
  ggplot(
    aes(y = hzn, x = mcra_copies_per_g, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  #facet_grid(rows = vars(site)) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per g soil",
    y = "Horizon"
  )

```


### texture-bulk-hzn averaged

```{r}
ddpcr_data_mcra_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    mcra_conc_av = mean(mcra_copies_per_g),
    mcra_conc_se = sd(mcra_copies_per_g) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mcra_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mcra_conc_av - mcra_conc_se, 
      xmax = mcra_conc_av + mcra_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per g soil",
    y = "Horizon"
  )
```

### Key take-aways (mcrA raw counts)

* Likely contamination in 2 of the samples, will need to re-run
* Obfuscates results for the B and C horizons


## Copies mcrA normalized to 16S copies 

### technical replicates averaged

```{r}
ddpcr_data_mcra_av %>% 
  #filter(!(samp %in% c("TC1", "RA1", "TB3") & bulk_agg == "B")) %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_mcra = mcra_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_mcra, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per 16S copy",
    y = "Horizon"
  )
```

### texture-bulk-hzn averaged

```{r}

ddpcr_data_mcra_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_mcra = mcra_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_mcra = mean(prop_mcra, na.rm = TRUE),
    se_prop_mcra = sd(prop_mcra) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_mcra, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_mcra - se_prop_mcra, 
      xmax = mean_prop_mcra + se_prop_mcra
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per 16S copy",
    y = "Horizon"
  )

```

### Key take-aways (mcrA normalized)

* In general, higher relative abundance of mcrA in surface horizons (if we ignore what is presumably an outlier)
* In A horizon:
** interior of aggregates has higher relative abundance of mcrA copies
** Loam has higher relative abundance of mcrA copies 

 

# gltA
Need to incorporate the gltA data from 27Feb2023

```{r}

ddpcr_data_glta <- 
  ddpcr_data_file_glta %>% 
  read_csv() %>% 
  filter(str_detect(TargetType, "Ch1")) %>% 
  separate(Sample, into = c("samp", "bulk_agg"), remove = FALSE) %>% 
  filter(!(samp %in% c("Water", "PositiveControl", "buffer"))) %>% 
  mutate(dilution = as.numeric(str_extract(Sample, "(?<=:)\\d+"))) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    glta_conc_unadj = Concentration,
    glta_droplets = AcceptedDroplets,
    glta_min = PoissonConfMin,
    glta_max = PoissonConfMax
  ) %>% 
  filter(glta_droplets > 10000) %>% 
  mutate(
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    across(c(glta_conc_unadj, dilution), as.numeric),
    glta_conc_adj = glta_conc_unadj * dilution * reaction_volume_df,
    across(c(glta_min, glta_max), ~. * dilution * reaction_volume_df)
  ) 
```
## Inspect technical replicates

```{r}

ddpcr_data_glta %>% 
  ggplot(
    aes(x = samp, y = glta_conc_adj, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = glta_min, ymax = glta_max))

```
Technical replicates look good. 

```{r}
ddpcr_data_glta_av <- 
  ddpcr_data_glta %>% 
  left_join(extraction_data, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    glta_copies_per_g =
      glta_conc_adj * dna_elution_volume / mass_extract_dry_g
  ) %>%   
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(c(glta_conc_adj, glta_copies_per_g), ~mean(., na.rm = TRUE))
  )

ddpcr_data_glta_av

```

## Copies per g

### Technical replicates averaged

```{r}
ddpcr_data_glta_av %>% 
  ggplot(
    aes(y = hzn, x = glta_copies_per_g, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
    scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  scale_y_discrete(limits = rev) +
  theme_bw() + 
  labs(
    x = "gltA copies per g soil",
    y = "Horizon"
  )

```


### texture-bulk-hzn averaged

```{r}
ddpcr_data_glta_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    glta_conc_av = mean(glta_copies_per_g, na.rm = TRUE),
    glta_conc_se = sd(glta_copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = glta_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = glta_conc_av - glta_conc_se, 
      xmax = glta_conc_av + glta_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "gltA copies per g soil",
    y = "Horizon"
  )
```


## Copies per 16S copy

### technical replicates averaged

```{r}
ddpcr_data_glta_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_glta = glta_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_glta, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "gltA copies per 16S copy",
    y = "Horizon"
  )
```


### texture-bulk-hzn averaged

```{r}

ddpcr_data_glta_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  filter(sixteenS_copies_per_g > 0) %>% 
  mutate(
    prop_glta = glta_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_glta = mean(prop_glta, na.rm = TRUE),
    se_prop_glta = sd(prop_glta, na.rm = TRUE) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_glta, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_glta - se_prop_glta, 
      xmax = mean_prop_glta + se_prop_glta
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "gltA copies per 16S copy",
    y = "Horizon"
  )

```

# nirK 

This code: 

* Imports the nirK data from a CSV
* Excludes 1:100 dilutions (which were too dilute)
* Corrects for DNA template dilution (1:10)
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)

```{r}

ddpcr_data_nirk <- 
  ddpcr_data_file_nirk %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg"), remove = FALSE) %>% 
  filter(!(samp %in% c("Water", "PositiveControl", "buffer"))) %>% 
  mutate(dilution = as.numeric(str_extract(Sample, "(?<=:)\\d+"))) %>% 
  filter(dilution == 10) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    nirk_conc_unadj = Concentration,
    nirk_droplets = AcceptedDroplets,
    nirk_min = PoissonConfMin,
    nirk_max = PoissonConfMax
  ) %>% 
  filter(nirk_droplets > 10000) %>% 
  mutate( #need to CONFIRM and switch out RC No Calls as Zeroes (no amplification)
    across(nirk_conc_unadj, ~if_else(. == "No Call", "0", .)),
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    across(c(nirk_conc_unadj, dilution), as.numeric),
    nirk_conc_adj = nirk_conc_unadj * dilution * reaction_volume_df,
    across(c(nirk_min, nirk_max), ~. * dilution * reaction_volume_df)
  ) 


ddpcr_data_nirk %>% arrange(nirk_conc_unadj)

#need to select appropriate dilution

```

## Inspect technical replicates

```{r}

ddpcr_data_nirk %>% 
  ggplot(
    aes(x = samp, y = nirk_conc_adj, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = nirk_min, ymax = nirk_max))

```

Technical replicates look good. RA2-IN is maybe a little funky, 

```{r}
ddpcr_data_nirk_av <- 
  ddpcr_data_nirk %>% 
  left_join(extraction_data, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    nirk_copies_per_g =
      nirk_conc_adj * dna_elution_volume / mass_extract_dry_g
  ) %>%   
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(c(nirk_conc_adj, nirk_copies_per_g), ~mean(.))
  )


ddpcr_data_nirk_av
```


## Copies per g

### Technical replicates averaged

```{r}
ddpcr_data_nirk_av %>% 
  ggplot(
    aes(y = hzn, x = nirk_copies_per_g, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
    scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  scale_y_discrete(limits = rev) +
  theme_bw() + 
  labs(
    x = "nirK copies per g soil",
    y = "Horizon"
  )

```


### texture-bulk-hzn averaged

```{r}
ddpcr_data_nirk_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    nirk_conc_av = mean(nirk_copies_per_g),
    nirk_conc_se = sd(nirk_copies_per_g) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = nirk_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = nirk_conc_av - nirk_conc_se, 
      xmax = nirk_conc_av + nirk_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per g soil",
    y = "Horizon"
  )
```

### Key take-aways (nirK raw counts)

* No difference between interior/exterior for nirK abundance
* nirK abundance decreases with depth 
* typically higher in Loam soils 

## Copies per 16S copy

### technical replicates averaged

```{r}
ddpcr_data_nirk_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirk = nirk_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_nirk, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per 16S copy",
    y = "Horizon"
  )
```


### texture-bulk-hzn averaged

```{r}

ddpcr_data_nirk_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirk = nirk_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_nirk = mean(prop_nirk, na.rm = TRUE),
    se_prop_nirk = sd(prop_nirk) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_nirk, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_nirk - se_prop_nirk, 
      xmax = mean_prop_nirk + se_prop_nirk
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per 16S copy",
    y = "Horizon"
  )

```

### Key take-aways (nirK normalized)

* Higher relative abundance in Sandy Loam soil than Loam soil 
* Interior of aggregates seemingly has higher relative abundance 
* No difference between interior/exterior for Loam soils

# nirS

This code: 

* Imports the nirS data from a CSV
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)

```{r}

ddpcr_data_nirs <- 
  ddpcr_data_file_nirs %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg"), remove = FALSE) %>% 
  filter(!(samp %in% c("Water", "PositiveControl", "buffer"))) %>% 
  mutate(dilution = as.numeric(str_extract(Sample, "(?<=:)\\d+"))) %>% 
  filter(str_detect(TargetType, "Ch1")) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    nirs_conc_unadj = Concentration,
    nirs_droplets = AcceptedDroplets,
    nirs_min = PoissonConfMin,
    nirs_max = PoissonConfMax
  ) %>% 
  filter(nirs_droplets > 10000, samp != "SF") %>% 
  mutate(
    across(nirs_conc_unadj, ~if_else(. == "No Call", "0", .)),
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    across(c(nirs_conc_unadj, dilution), as.numeric),
    nirs_conc_adj = nirs_conc_unadj * dilution * reaction_volume_df,
    across(c(nirs_min, nirs_max), ~. * dilution * reaction_volume_df)
  ) 


ddpcr_data_nirs


```


## Inspect technical replicates

```{r}

ddpcr_data_nirs %>% 
  filter(site == "T") %>% 
  mutate(across(dilution, as.factor)) %>% 
  ggplot(
    aes(x = samp, y = nirs_conc_adj, color = bulk_agg, shape = dilution)
  ) +
  geom_pointrange(aes(ymin = nirs_min, ymax = nirs_max)) 

```


```{r}
ddpcr_data_nirs %>% 
  mutate(across(dilution, as.factor)) %>% 
  filter(site == "R") %>% 
  ggplot(
    aes(x = samp, y = nirs_conc_adj, color = bulk_agg, shape = dilution)
  ) +
  geom_pointrange(aes(ymin = nirs_min, ymax = nirs_max)) 
```

The technical replicates are at least relatively close even compared to the dilutions. Going to retain the un-diluted samples for this run. 

```{r}
ddpcr_data_nirs_av <- 
  ddpcr_data_nirs %>% 
  filter(dilution != 10) %>% 
  left_join(extraction_data, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    nirs_copies_per_g =
      nirs_conc_adj * dna_elution_volume / mass_extract_dry_g
  ) %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(c(nirs_conc_adj, nirs_copies_per_g), ~mean(., na.rm = TRUE))
  )


ddpcr_data_nirs_av
```

```{r}
ddpcr_data_nirs_av %>% 
  ggplot(
    aes(y = hzn, x = nirs_copies_per_g, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
    scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  scale_y_discrete(limits = rev) +
  theme_bw() + 
  labs(
    x = "nirS copies per g soil",
    y = "Horizon"
  )

```

```{r}
ddpcr_data_nirs_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    nirs_conc_av = mean(nirs_copies_per_g),
    nirs_conc_se = sd(nirs_copies_per_g) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = nirs_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = nirs_conc_av - nirs_conc_se, 
      xmax = nirs_conc_av + nirs_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per g soil",
    y = "Horizon"
  )
```


## Copies per 16S copy

### technical replicates averaged

```{r}
ddpcr_data_nirs_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirs = nirs_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_nirs, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirS copies per 16S copy",
    y = "Horizon"
  )
```


### texture-bulk-hzn averaged

```{r}

ddpcr_data_nirs_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirs = nirs_copies_per_g / sixteenS_copies_per_g
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_nirs = mean(prop_nirs, na.rm = TRUE),
    se_prop_nirs = sd(prop_nirs) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_nirs, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_nirs - se_prop_nirs, 
      xmax = mean_prop_nirs + se_prop_nirs
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirS copies per 16S copy",
    y = "Horizon"
  )

```
# All Genes 

## Combine data

NOTE: Only 19 samples have a complete dataset for all the genes and 16S

```{r}

ddpcr_compiled <- 
  ddpcr_data_nirs_av %>% 
  full_join(ddpcr_data_nirk_av, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  full_join(ddpcr_data_glta_av, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  full_join(ddpcr_data_mcra_av, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  full_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    total_anaerobe_copies = 
      nirs_copies_per_g + nirk_copies_per_g + mcra_copies_per_g + glta_copies_per_g
  ) 


```

```{r}

ddpcr_compiled %>% 
  ggplot(
    aes(y = hzn, x = total_anaerobe_copies, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK+nirS+gltA+mcrA copies per g soil",
    y = "Horizon"
  )

```


```{r}
ddpcr_compiled %>% 
  mutate(
    prop_anaerobe = total_anaerobe_copies / sixteenS_copies_per_g
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_anaerobe, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "(nirK+nirS+gltA+mcrA) per 16S",
    y = "Horizon"
  )
```


```{r}
ddpcr_compiled %>% 
  mutate(
    prop_anaerobe = total_anaerobe_copies / sixteenS_copies_per_g
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_an = mean(prop_anaerobe, na.rm = TRUE),
    se_prop_an = sd(prop_anaerobe) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_an, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_an - se_prop_an, 
      xmax = mean_prop_an + se_prop_an
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "(nirK+nirS+gltA+mcrA) per 16S",
    y = "Horizon"
  )

```

# Stacked Bar Charts

## Copies per g soil


```{r}

ddpcr_stacked_bar_data <-
  ddpcr_compiled %>% 
  select(-c(contains("conc"), total_anaerobe_copies)) %>% 
  pivot_longer(
    cols = contains("copies_per_g"),
    names_to = "target_gene",
    values_to = "copies_per_g"
  ) %>% 
  mutate(across(target_gene, ~str_extract(.,"nirs|nirk|glta|mcra|sixteenS")))

```

### 16S

```{r}
ddpcr_stacked_bar_data %>% 
  filter(target_gene == "sixteenS") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_g = mean(copies_per_g, na.rm = TRUE),
    se_copies_per_g = sd(copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_g,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_g, xmax = avg_copies_per_g + se_copies_per_g),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per g soil"
  )
```


### nirS

```{r}
ddpcr_stacked_bar_data %>% 
  filter(target_gene == "nirs") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_g = mean(copies_per_g, na.rm = TRUE),
    se_copies_per_g = sd(copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_g,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_g, xmax = avg_copies_per_g + se_copies_per_g),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per g soil"
  )
```

### nirK

```{r}
ddpcr_stacked_bar_data %>% 
  filter(target_gene == "nirk") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_g = mean(copies_per_g, na.rm = TRUE),
    se_copies_per_g = sd(copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_g,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_g, xmax = avg_copies_per_g + se_copies_per_g),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per g soil"
  )
```

### gltA

```{r}
ddpcr_stacked_bar_data %>% 
  filter(target_gene == "glta") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_g = mean(copies_per_g, na.rm = TRUE),
    se_copies_per_g = sd(copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_g,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_g, xmax = avg_copies_per_g + se_copies_per_g),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per g soil"
  )
```

### mcrA

```{r}
ddpcr_stacked_bar_data %>% 
  filter(target_gene == "mcra") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_g = mean(copies_per_g, na.rm = TRUE),
    se_copies_per_g = sd(copies_per_g, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_g,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_g, xmax = avg_copies_per_g + se_copies_per_g),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per g soil"
  )
```

## Copies normalized to 16S


```{r}

sixteenS_abund <- 
  ddpcr_stacked_bar_data %>% 
  filter(target_gene == "sixteenS") %>% 
  select(-target_gene) %>% 
  rename(sixteenS_copies_per_g = copies_per_g)


ddpcr_stacked_bar_prop_data <- 
  ddpcr_stacked_bar_data %>% 
  left_join(sixteenS_abund, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    copies_per_16S = copies_per_g / sixteenS_copies_per_g
  )

```



### nirS

```{r}
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene == "nirs") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_16S = mean(copies_per_16S, na.rm = TRUE),
    se_copies_per_16S = sd(copies_per_16S, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_16S,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_16S, xmax = avg_copies_per_16S + se_copies_per_16S),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per 16S copy"
  )
```

### nirK

```{r}
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene == "nirk") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  summarise(
    avg_copies_per_16S = mean(copies_per_16S, na.rm = TRUE),
    se_copies_per_16S = sd(copies_per_16S, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_16S,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_16S, xmax = avg_copies_per_16S + se_copies_per_16S),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per 16S copy"
  )
```

### gltA

```{r}
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene == "glta") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  filter(copies_per_16S != Inf) %>% 
  summarise(
    avg_copies_per_16S = mean(copies_per_16S, na.rm = TRUE),
    se_copies_per_16S = sd(copies_per_16S, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_16S,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_16S, xmax = avg_copies_per_16S + se_copies_per_16S),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per 16S copy"
  )
```

### mcrA

```{r}
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene == "mcra") %>% 
  group_by(site, hzn, bulk_agg, target_gene) %>% 
  filter(copies_per_16S != Inf) %>% 
  summarise(
    avg_copies_per_16S = mean(copies_per_16S, na.rm = TRUE),
    se_copies_per_16S = sd(copies_per_16S, na.rm = TRUE) / sqrt(n())
  ) %>% 
  mutate(
    site_bulk_agg = 
      factor(
        str_c(site, bulk_agg), 
        levels = c("TIN", "TB", "RB", "RIN")
      )
  ) %>% 
  ggplot(
    aes(
      x = avg_copies_per_16S,
      y = hzn,
      fill = site,
      alpha = fct_rev(bulk_agg)
    )
  ) + 
  geom_col(position = "dodge") + 
  geom_errorbarh(
    aes(xmin = avg_copies_per_16S, xmax = avg_copies_per_16S + se_copies_per_16S),
    position = "dodge"
  ) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    y = "Horizon",
    x = "Copies per 16S copy"
  )
```

### Totals

```{r}
ddpcr_stacked_bar_prop_data
```


```{r}

  
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene != "sixteenS") %>% 
  ggplot(
    aes(y = bulk_agg, x = copies_per_g, alpha = bulk_agg, fill = target_gene)
  ) +
  geom_col() +
  scale_y_discrete(limits = rev) + 
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  facet_grid(cols = vars(site), rows = vars(hzn)) +
  theme_bw() + 
  labs(
    x = "nirK+nirS+gltA+mcrA copies per g soil",
    y = "Horizon"
  )
  
  


```


```{r}
  
ddpcr_stacked_bar_prop_data %>% 
  filter(target_gene != "sixteenS", copies_per_16S != Inf) %>% 
  ggplot(
    aes(y = bulk_agg, x = copies_per_16S, alpha = bulk_agg, fill = target_gene)
  ) +
  geom_col() +
  scale_y_discrete(limits = rev) + 
  scale_alpha_manual(
    values = agg_alpha,
    labels = agg_names,
    name = NULL
  ) +
  facet_grid(cols = vars(site), rows = vars(hzn)) +
  theme_bw() + 
  labs(
    x = "nirK+nirS+gltA+mcrA copies per 16S",
    y = "Horizon"
  )
```



