---
title: "ddpcr-16s"
author: "Emily Lacroix"
date: "2022-10-26"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set-up

## Libraries

```{r}
library(tidyverse)
library(readxl)
```


## Files

```{r}

ddpcr_data_file_16s <- "/Users/emily/Documents/Research/Aggregates-Meret/Data/ddPCR/EML_16s_09sep2022-manual.csv" 

ddpcr_data_file_mcra <- 
  "/Users/emily/Documents/Research/Aggregates-Meret/Data/ddPCR/EML_mcrA_01sep2022-manual.csv"

ddpcr_data_file_glta <- 
  "/Users/emily/Documents/Research/Aggregates-Meret/Data/ddPCR/22Oct22_gltA/AMG_glta_22oct2022_all_manual.csv"

ddpcr_data_file_nirk <- "/Users/emily/Documents/Research/Aggregates-Meret/Data/ddPCR/AG_nirK_1_12_23.csv"

#dna_extraction_file <- 


```


## Constants

```{r}

reaction_volume_df <- 25 #NEED TO INCORPORATE INTO MEASUREMENTS

site_colors <- c("R" = "darkgoldenrod1", "T" = "darkblue")

site_names <- c("R" = "Sandy Loam", "T" = "Loam")

agg_names <- c("B" = "Bulk soil", "IN" = "Agg. Interior")

agg_shapes <- c("B" = 15, "IN" = 17)


# g_h2o = mass_g / (1 / avg_gwc + 1),
# mass_dry_soil = mass_g - g_h2o,
# prop = conc / sixteenS_conc,
# copies_per_g_sixteenS = sixteenS_conc * 100 / mass_dry_soil,
# copies_per_g = conc * 100 / mass_dry_soil


```


# 16S

This code: 

* Imports the 16S data from a CSV

```{r}

sixteenS_df <- 1000 #NEED TO DOUBLE CHECK WITH DDPCR BINDER

ddpcr_data_16s <- 
  ddpcr_data_file_16s %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg", "dilution")) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    sixteenS_conc = Concentration,
    sixteenS_min = PoissonConfMin,
    sixteenS_max = PoissonConfMax,
    droplets = AcceptedDroplets
  ) %>% 
  filter(
    !(
      is.na(dilution) & 
        samp %in% c("RA3", "RB1", "RB2", "RB3") & 
        bulk_agg == "IN"
      )
  )


```


## Check Technical replicates
```{r}

ddpcr_data_16s %>% 
  ggplot(
    aes(x = samp, y = sixteenS_conc, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = sixteenS_min, ymax = sixteenS_max))

```

Technical replicate for TA1 does not look great. Other ones look good though. 

## Adjust conc

This code: 

* Subtracts the counts from the blanks 
* Corrects for DNA template dilution
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)
* Takes average value for technical replicates

```{r}
blank_16s <- 
  ddpcr_data_16s %>% 
  filter(samp == "TE" | samp == "Water") %>% 
  summarise(mean_blank_16s = mean(sixteenS_conc)) %>% 
  pull(mean_blank_16s)


data_16s_adj <- 
  ddpcr_data_16s %>% 
  filter(samp != "TE" & samp != "Water") %>% 
  mutate(
    blank = blank_16s,
    sixteenS_conc_minus_blank =
      case_when(
        dilution == "1" ~ (sixteenS_conc / 10) - blank,
        TRUE ~ sixteenS_conc - blank
      ),
    across(sixteenS_conc_minus_blank, ~ if_else(. < 0, 0, .)),
    sixteenS_conc_adj = 
      #already accounts for 100 vs. 1000 dilution
      sixteenS_conc_minus_blank * sixteenS_df * reaction_volume_df, 
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = str_extract(samp, ".{1}$")
  ) %>% 
  select(
    site, hzn, rep, bulk_agg, sixteenS_conc_adj, 
    sixteenS_droplets = droplets
  ) %>% 
  mutate(across(rep, as.integer)) %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(sixteenS_conc_adj, ~mean(.))
  )

```

It appears we got no positive amplification (beyond contamination) from RC1-Bulk. I think we'll need to try again or omit from dataset. 

## Copies per g

### technical replicates averaged
```{r}

data_16s_adj %>% 
  ggplot(
    aes(y = hzn, x = sixteenS_conc_adj, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "16S copies per uL extract",
    y = "Horizon"
  )

```

### texture-bulk-hzn averaged

```{r}
data_16s_adj %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_16s = mean(sixteenS_conc_adj, na.rm = TRUE),
    se_16s = sd(sixteenS_conc_adj) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_16s, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(xmin = mean_16s - se_16s, xmax = mean_16s + se_16s),
    fatten = 4
  ) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "16S copies per uL extract",
    y = "Horizon"
  )

```


### Key take-aways (16S)

* More 16S copies in Loam vs. Sandy Loam soil
* More 16S copies in surface soil & decreases with depth
* Aggregate interiors yield less 16S copies, unclear if this is due to extraction mass or efficiency....


# mcrA

This code: 

* Imports the mcrA data from a CSV
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)

NOTE - one of my technical replicates is really high....need to look at notes from the ddPCR run


```{r}

ddpcr_data_mcra <- 
  ddpcr_data_file_mcra %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg")) %>% 
  select(
    samp, 
    bulk_agg, 
    mcra_conc = Concentration,
    mcra_min = PoissonConfMin,
    mcra_max = PoissonConfMax,
    droplets = AcceptedDroplets
  ) %>% 
  filter(
    !(samp %in% c("Water", "PositiveControl", "buffer")),
    droplets > 10000
  ) %>% 
  mutate(
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    mcra_droplets = droplets,
    across(mcra_conc, as.numeric),
    across(c(mcra_conc, mcra_min, mcra_max), ~ . * reaction_volume_df)
  ) 

ddpcr_data_mcra 
  
```

## Inspect techincal replicates

```{r}

ddpcr_data_mcra %>% 
  ggplot(
    aes(x = samp, y = mcra_conc, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = mcra_min, ymax = mcra_max))

```

RC1-Bulk is seemingly missing..... and the technical replicates for RA1 look horrible. Need to look at ddPCR folder. 

For now, let's average the technical replicates

This code

* Takes average value for technical replicates


```{r}

ddpcr_data_mcra_av <- 
  ddpcr_data_mcra %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(mcra_conc, ~mean(.))
  )
```


## Copies per g 

### technical replicates averaged

```{r}

ddpcr_data_mcra_av %>% 
  ggplot(
    aes(y = hzn, x = mcra_conc, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  #facet_grid(rows = vars(site)) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per uL extract",
    y = "Horizon"
  )

```


### texture-bulk-hzn averaged

```{r}
ddpcr_data_mcra_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    mcra_conc_av = mean(mcra_conc),
    mcra_conc_se = sd(mcra_conc) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mcra_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mcra_conc_av - mcra_conc_se, 
      xmax = mcra_conc_av + mcra_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per uL extract",
    y = "Horizon"
  )
```

### Key take-aways (mcrA raw counts)

* Likely contamination in 2 of the samples, will need to re-run
* Obfuscates results for the B and C horizons


## Copies mcrA normalized to 16S copies 

### technical replicates averaged

```{r}
ddpcr_data_mcra_av %>% 
  #filter(!(samp %in% c("TC1", "RA1", "TB3") & bulk_agg == "B")) %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_mcra = mcra_conc / sixteenS_conc_adj
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_mcra, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per 16S copy",
    y = "Horizon"
  )
```

### texture-bulk-hzn averaged

```{r}

ddpcr_data_mcra_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_mcra = mcra_conc / sixteenS_conc_adj
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_mcra = mean(prop_mcra, na.rm = TRUE),
    se_prop_mcra = sd(prop_mcra) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_mcra, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_mcra - se_prop_mcra, 
      xmax = mean_prop_mcra + se_prop_mcra
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "mcrA copies per 16S copy",
    y = "Horizon"
  )

```

### Key take-aways (mcrA normalized)

* In general, higher relative abundance of mcrA in surface horizons (if we ignore what is presumably an outlier)
* In A horizon:
** interior of aggregates has higher relative abundance of mcrA copies
** Loam has higher relative abundance of mcrA copies 

 

# gltA

NOTE - we got like no positive amplification for gltA....probably because the droplets sat for like 8 days 


# nirK 

This code: 

* Imports the nirK data from a CSV
* Excludes 1:100 dilutions (which were too dilute)
* Corrects for DNA template dilution (1:10)
* Corrects for reaction volume dilution (reports concentration in copies / uL DNA extract)

```{r}

#nirk_df <- 10

ddpcr_data_nirk <- 
  ddpcr_data_file_nirk %>% 
  read_csv() %>% 
  separate(Sample, into = c("samp", "bulk_agg"), remove = FALSE) %>% 
  filter(!(samp %in% c("Water", "PositiveControl", "buffer"))) %>% 
  mutate(dilution = as.numeric(str_extract(Sample, "(?<=:)\\d+"))) %>% 
  filter(dilution == 10) %>% 
  select(
    samp, 
    bulk_agg, 
    dilution,
    nirk_conc_unadj = Concentration,
    nirk_droplets = AcceptedDroplets,
    nirk_min = PoissonConfMin,
    nirk_max = PoissonConfMax
  ) %>% 
  filter(nirk_droplets > 10000) %>% 
  mutate( #need to CONFIRM and switch out RC No Calls as Zeroes (no amplification)
    across(nirk_conc_unadj, ~if_else(. == "No Call", "0", .)),
    site = str_extract(samp, ".{1}"),
    hzn = str_extract(samp, ".{1}(?=\\d)"),
    rep = as.integer(str_extract(samp, ".{1}$")),
    across(c(nirk_conc_unadj, dilution), as.numeric),
    nirk_conc_adj = nirk_conc_unadj * dilution * reaction_volume_df,
    across(c(nirk_min, nirk_max), ~. * dilution * reaction_volume_df)
  ) 


ddpcr_data_nirk %>% arrange(nirk_conc_unadj)

#need to select appropriate dilution

```

## Inspect technical replicates

```{r}

ddpcr_data_nirk %>% 
  ggplot(
    aes(x = samp, y = nirk_conc_adj, color = bulk_agg)
  ) +
  geom_pointrange(aes(ymin = nirk_min, ymax = nirk_max))

```

Technical replicates look good. RA2-IN is maybe a little funky, 





```{r}
ddpcr_data_nirk_av <- 
  ddpcr_data_nirk %>% 
  group_by(site, hzn, rep, bulk_agg) %>%
  summarise(
    across(nirk_conc_adj, ~mean(.))
  )


ddpcr_data_nirk_av
```


## Copies per g

### Technical replicates averaged

```{r}
ddpcr_data_nirk_av %>% 
  ggplot(
    aes(y = hzn, x = nirk_conc_adj, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
    scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  scale_y_discrete(limits = rev) +
  theme_bw() + 
  labs(
    x = "nirK copies per uL extract",
    y = "Horizon"
  )

```


### texture-bulk-hzn averaged

```{r}
ddpcr_data_nirk_av %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarize(
    nirk_conc_av = mean(nirk_conc_adj),
    nirk_conc_se = sd(nirk_conc_adj) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = nirk_conc_av, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = nirk_conc_av - nirk_conc_se, 
      xmax = nirk_conc_av + nirk_conc_se)
  ) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per uL extract",
    y = "Horizon"
  )
```

### Key take-aways (nirK raw counts)

* No difference between interior/exterior for nirK abundance
* nirK abundance decreases with depth 
* typically higher in Loam soils 

## Copies per 16S copy

### technical replicates averaged

```{r}
ddpcr_data_nirk_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirk = nirk_conc_adj / sixteenS_conc_adj
  ) %>% 
  ggplot(
    aes(y = hzn, x = prop_nirk, shape = bulk_agg, color = site)
  ) +
  geom_point(size = 3) +
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per 16S copy",
    y = "Horizon"
  )
```


### texture-bulk-hzn averaged

```{r}

ddpcr_data_nirk_av %>% 
  left_join(data_16s_adj, by = c("site", "hzn", "rep", "bulk_agg")) %>% 
  mutate(
    prop_nirk = nirk_conc_adj / sixteenS_conc_adj
  ) %>% 
  group_by(site, hzn, bulk_agg) %>% 
  summarise(
    mean_prop_nirk = mean(prop_nirk, na.rm = TRUE),
    se_prop_nirk = sd(prop_nirk) / sqrt(n())
  ) %>% 
  ggplot(
    aes(y = hzn, x = mean_prop_nirk, shape = bulk_agg, color = site)
  ) +
  geom_pointrange(
    aes(
      xmin = mean_prop_nirk - se_prop_nirk, 
      xmax = mean_prop_nirk + se_prop_nirk
    )
  ) + 
  scale_y_discrete(limits = rev) + 
  scale_color_manual(
    values = site_colors,
    labels = site_names,
    name = "Texture"
  ) +
  scale_shape_manual(
    values = agg_shapes,
    labels = agg_names,
    name = NULL
  ) +
  theme_bw() + 
  labs(
    x = "nirK copies per 16S copy",
    y = "Horizon"
  )

```

### Key take-aways (nirK normalized)

* Higher relative abundance in Sandy Loam soil than Loam soil 
* Interior of aggregates seemingly has higher relative abundance 
* No difference between interior/exterior for Loam soils

